Baby mental life: fPCA

### 2025-02-14 supplement/supplement-main_anonymized.Rmd
revisions for R&R

---
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover_anonymized.tex
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 2
    number_sections: false
  #   reference_docx: word-styles-ref.docx
  # word_document:
bibliography: "references.bib"
csl: apa.csl
# cls: article.cls
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \modulolinenumbers[5]
   - \usepackage{float}
   - \usepackage{url}
   - \usepackage{pdflscape}
tables: yes
---

@@

```{r load packages}
library(ggdendro)
library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(cowplot)
library(tidyverse)
library(rsq)
library(ggnewscale)
```

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.

@@

To our knowledge, there is currently no consensus about how to account for within-participant variance alongside between-participant variance in the context of exploratory factor analysis or similar dimensionality reduction analyses. Thus, to conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each. (See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].

@@

```{r fig01, fig.cap="Study 1, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
# knitr::include_graphics("../outputs/fig01.pdf")
```

@@

```{r figS01 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s1_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS01.pdf")) {
  ggsave("../outputs/figS01.svg")
  ggsave("../outputs/figS01.pdf")
}
```

```{r figS01, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS01.pdf")
```

@@

```{r figS02 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s1_efa_wdm)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS02.pdf")) {
  ggsave("../outputs/figS02.svg")
  ggsave("../outputs/figS02.pdf")
}
```

```{r figS02, fig.cap="Study 1, factor solution suggested by minimizing BIC."}
knitr::include_graphics("../outputs/figS02.pdf")
```

@@

Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life. Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life. To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensation_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age. As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensation_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.

@@

```{r figS03 code, fig.width = 8, fig.asp = 0.5}
d1_gam %>%
  group_by(ResponseId, target_year, factor) %>%
  # # ALTERNATIVE: take just top 5 items per factor (like Study 2)
  # left_join(d1_scales %>% distinct(factor, capacity, loading)) %>%
  # top_n(5, loading) %>%
  summarise(score = mean(response, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = target_year, y = score, color = factor)) +
  facet_grid(~ factor) +
  geom_path(aes(group = ResponseId),
            # color = "#160072",
            alpha = 0.2, size = 0.02) +
  geom_path(
    data = . %>%
      group_by(factor, target_year) %>%
      summarise(mean = mean(score, na.rm = T)) %>%
      ungroup,
    aes(y = mean),
    color = "black", lty = 2) +
  geom_pointrange(
    data = . %>%
      group_by(factor, target_year) %>%
      multi_boot_standard(col = "score") %>%
      ungroup,
    aes(y = mean, ymin = ci_lower, ymax = ci_upper),
    color = "black",
    fatten = 1) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = seq(0, 100, 25)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Mean response\n0 = not at all capable, 100 = completely capable") +
  guides(color = guide_none())

# save plot
if (resave_plots == T | !file.exists("../outputs/figS03.pdf")) {
  ggsave("../outputs/figS03.svg")
  ggsave("../outputs/figS03.pdf")
}
```

```{r figS03, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1). Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
knitr::include_graphics("../outputs/figS03.pdf")
```

@@

```{r figS04 code, fig.width = 9, fig.asp = 0.5}
heatmap_fun(s2_efa_par, 
            factor_names = c("Negative affect",
                             "Cognition and control",
                             "Bodily sensation",
                             "Social connection"))

# save plot
if (resave_plots == T | !file.exists("../outputs/figS04.pdf")) {
  ggsave("../outputs/figS04.svg")
  ggsave("../outputs/figS04.pdf")
}
```

```{r figS04, fig.cap="Study 2, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
# knitr::include_graphics("../outputs/figS04.pdf")
```

@@

```{r figS05 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s2_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS05.pdf")) {
  ggsave("../outputs/figS05.svg")
  ggsave("../outputs/figS05.pdf")
}
```

```{r figS05, fig.cap="Study 2, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS05.pdf")
```

@@

```{r s2 scales}
d2_scales <- s2_efa_par$loadings[] %>%
  data.frame() %>%
  rownames_to_column("capacity") %>%
  gather(factor, loading, -capacity) %>%
  group_by(capacity) %>%
  top_n(1, loading) %>%
  ungroup() %>%
  mutate(factor = recode_factor(
    factor,
    "MR3" = "Bodily sensation",
    "MR1" = "Negative affect",
    "MR4" = "Social connection",
    "MR2" = "Cognition and control")) %>%
  arrange(factor, desc(loading)) %>%
  mutate(order = 1:nrow(.))
```

@@

@@

# Study comparison: Capacity attributions to newborns, 9-months, and 5-year-olds

@@

To provide some sense of the stability and reliability of US adults' representations of specific target ages across studies, Supplementary Figure \@ref(fig:figS06) presents a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds). As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here. In Study 2, participants assessed the 20 capacities depicted in Panel A, at 13 target ages (including but not limited to the 3 target ages depicted here). In Study 3, participants assessed 8 capacities (a subset of the 20 capacities depicted in Panel A), at 13 target ages (including but not limited to the 3 target ages depicted here).

>>>>

---
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover_anonymized.tex
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 2
    number_sections: false
  #   reference_docx: word-styles-ref.docx
  # word_document:
bibliography: "references.bib"
csl: apa.csl
# cls: article.cls
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \modulolinenumbers[5]
   - \usepackage{float}
   - \usepackage{url}
   - \usepackage{pdflscape}
   - \makeatletter
   - \renewcommand{\fnum@figure}{Figure S\thefigure}
   - \makeatother
tables: yes
---

@@

```{r load packages}
# library(ggdendro)
# library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(cowplot)
# library(fda)
library(rsq)
library(ggnewscale)
library(GGally)
library(ggrepel)
library(igraph)
library(ggraph)
library(tidyverse)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
```

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" and "bookdown" packages for R [@xie2016; @xie2021; @xie2024]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document (supplement-main.Rmd), which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.

@@

Traditional exploratory factor analysis techniques are not equipped to account for within-participant variance alongside between-participant variance. To conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each. See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA; but see also [@owen.wang2016] for a bi-cross-validation technique, which might be adapted to address this repeated-measures design by structuring cross-validation folds to exclude all observations from a given participant within a given fold. (We thank a helpful reviewer for this suggestion.)

We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].

@@

```{r fig01, fig.cap="Study 1, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)", include = F}
knitr::include_graphics("../outputs/fig01.pdf")
```

```{r figS01 code, fig.width = 8, fig.asp = 0.8}
# custom density function with adjustable smoothing
density_fn <- function(data, mapping, adj_val = 3, ...) {
  filtered_data <- data %>%
    filter(!is.na(factor))

  ggplot(filtered_data, mapping) +
    geom_density(
      aes(color = factor, fill = factor),
      alpha = 0.2, adjust = adj_val, inherit.aes = TRUE, ...)  # adjust controls smoothness
}

# custom points function with horizontal line
points_fn <- function(data, mapping, ...) {
  ggplot(data, mapping) +
    geom_hline(
      yintercept = 0, 
      linetype = "dashed", 
      color = "black",
      size = 0.3) +
    geom_point(
      aes(color = factor, fill = factor),
      alpha = 0.9, size = 1, inherit.aes = TRUE, ...)
}

# plot
ggpairs(
  legend = c(2, 1),
  switch = "both",
  s1_efa_par$loadings[] %>%
    data.frame() %>%
    rownames_to_column("capacity") %>%
    mutate(
      # a priori sorting of capacities (for Studies 2-3)
      factor = case_when(
        capacity %in% c(
          "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
          "feeling_physically_uncomfortable") ~ "Bodily sensation",
        capacity %in% c(
          "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
          "feeling_helpless", "feeling_lonely") ~ "Negative affect",
        capacity %in% c(
          "feeling_happy", "finding_something_funny", "feeling_excited",
          "loving_somebody", "learning_from_other_people") ~ "Social connection",
        capacity %in% c(
          "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
          "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
    mutate(factor = factor(
      factor, 
      levels = c(
        "Bodily sensation", "Negative affect", 
        "Social connection", "Cognition and control"))) %>%
    mutate(capacity = gsub("_", " ", capacity)) %>%
    select(MR2, MR4, MR3, MR1, everything()) %>%
    rename(`Cognition and control` = MR1,
           `Bodily sensation` = MR2,
           `Social connection` = MR3,
           `Negative affect` = MR4),
  aes(color = factor, fill = factor),
  columns = 1:4,
  # upper = list(continuous = text_fn_filtered),
  upper = list(continuous = points_fn),
  lower = list(continuous = points_fn),
  # diag = list(continuous = ggally_densityDiag),
  diag = list(continuous = density_fn),
  # diag = "blank",
  showStrips = TRUE
) +
  geom_vline(xintercept = 0, lty = 2, color = "black", size = 0.3) +
  # geom_hline(yintercept = 0, lty = 2, color = "black", size = 0.3) +
  scale_color_viridis_d(
    name = "Domain (Studies 2-3):",
    end = 0.9, option = "viridis",
    na.value = "gray80",
    labels = c(
      "Bodily sensation", "Negative affect", 
      "Social connection", "Cognition and control", 
      "Not used in Studies 2-3"),
    aesthetics = c("color", "fill")
  ) +
  scale_x_continuous(breaks = seq(-100, 100, 100)) +
  scale_y_continuous(breaks = seq(-100, 100, 100)) +
  guides(color = guide_legend(override.aes = list(size = 3)),
         fill = guide_legend(override.aes = list(size = 3))) +
  # labs(color = "Domain (Studies 2-3):", fill = "Domain (Studies 2-3):") +
  theme_minimal() +
  theme(panel.border = element_rect(fill = NA, color = "black"),
        panel.grid = element_blank(),
        strip.placement = "outside",
        legend.position = "right")

# save plot
if (resave_plots == T | !file.exists("../outputs/figS01.pdf")) {
  ggsave("../outputs/figS01.jpg")
  ggsave("../outputs/figS01.svg")
  ggsave("../outputs/figS01.pdf")
}
```

```{r figS01, fig.cap="Study 1, scatterplot matrix ('pairs plot') visualizing the relationships among factor loadings and the distributions of factor loadings across items for the four-factor solution suggested by parallel analysis (loadings presented in Figure 1). Along the diagonal are density plots showing, for each of the four factors, the distribution of factor loadings for the subset of capacities later used to represent each 'domain' in Studies 2-3. Panels in the upper and lower triangles are scatterplots of factor loadings on each pair of factors, including all of the capacities included in Study 1.", include = T}
knitr::include_graphics("../outputs/figS01.pdf")
```

```{r figS02 function, fig.width = 10}
figS02_fun <- function(domain1, domain2) {

  domain1 <- sym(domain1)
  domain2 <- sym(domain2)

  d <- s1_efa_par$loadings[] %>%
    data.frame() %>%
    rownames_to_column("capacity") %>%
    mutate(
      factor = case_when(
        capacity %in% c(
          "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
          "feeling_physically_uncomfortable") ~ "Bodily sensation",
        capacity %in% c(
          "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
          "feeling_helpless", "feeling_lonely") ~ "Negative affect",
        capacity %in% c(
          "feeling_happy", "finding_something_funny", "feeling_excited",
          "loving_somebody", "learning_from_other_people") ~ "Social connection",
        capacity %in% c(
          "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
          "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
    mutate(factor = factor(
      factor, 
      levels = c(
        "Bodily sensation", "Negative affect", 
        "Social connection", "Cognition and control"))) %>%
    mutate(capacity = gsub("_", " ", capacity)) %>%
    # gather(factor, loading, starts_with("MR")) %>%
    rename("Cognition and control" = MR1,
           "Bodily sensation" = MR2,
           "Social connection" = MR3,
           "Negative affect" = MR4)

  p <- d %>%
    ggplot(aes(x = !!domain1,
               y = !!domain2)) +
    geom_hline(yintercept = 0, lty = 2) +
    geom_vline(xintercept = 0, lty = 2) +
    geom_point(aes(color = factor)) +
    ggrepel::geom_text_repel(
      aes(label = capacity,
          color = factor),
      show.legend = F,
      size = 3) +
    # geom_text(aes(label = capacity)) +
    scale_color_viridis_d(
      name = "Domain (Studies 2-3):",
      end = 0.9, option = "viridis", na.value = "gray70",
      labels = c("Bodily sensation", "Negative affect", 
                 "Social connection", "Cognition and control",
                 "Not included in Studies 2-3")
    ) +
    scale_x_continuous(breaks = seq(-1, 1, 0.2)) +
    scale_y_continuous(breaks = seq(-1, 1, 0.2)) +
    coord_fixed() +
    theme_minimal()

  print(p)
}
```

```{r figS02 code, fig.width = 10}
for(i in c("Bodily sensation", "Negative affect", 
           "Social connection", "Cognition and control")) {
  for(j in c("Bodily sensation", "Negative affect", 
             "Social connection", "Cognition and control")) {
    if(i != j) {
      figS02_fun(i, j)

      # save plot
      if (resave_plots == T | !file.exists(
        paste0("../outputs/figS02_",
               gsub(" ", "-", tolower(i)), "_",
               gsub(" ", "-", tolower(j)),
               ".pdf"))) {
        ggsave(
          paste0("../outputs/figS02_",
                 gsub(" ", "-", tolower(i)), "_",
                 gsub(" ", "-", tolower(j)),
                 ".jpg"))
        ggsave(
          paste0("../outputs/figS02_",
                 gsub(" ", "-", tolower(i)), "_",
                 gsub(" ", "-", tolower(j)),
                 ".svg"))
        ggsave(
          paste0("../outputs/figS02_",
                 gsub(" ", "-", tolower(i)), "_",
                 gsub(" ", "-", tolower(j)),
                 ".pdf"))
      }
    }
  }
}
```

```{r figS02, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'negative affect' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_bodily-sensation_negative-affect.pdf")
```

```{r figS03, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'social connection' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_bodily-sensation_social-connection.pdf")
```

```{r figS04, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_bodily-sensation_cognition-and-control.pdf")
```

```{r figS05, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'negative affect' and 'social connection' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_negative-affect_cognition-and-control.pdf")
```

```{r figS06, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'negative affect' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_negative-affect_cognition-and-control.pdf")
```

```{r figS07, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'social connection' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1). The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
knitr::include_graphics("../outputs/figS02_social-connection_cognition-and-control.pdf")
```

@@

```{r figS08 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s1_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS08.pdf")) {
  ggsave("../outputs/figS08.svg")
  ggsave("../outputs/figS08.pdf")
}
```

```{r figS08, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS08.pdf")
```

@@

```{r figS09 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s1_efa_wdm)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS09.pdf")) {
  ggsave("../outputs/figS09.svg")
  ggsave("../outputs/figS09.pdf")
}
```

```{r figS09, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS09.pdf")
```

@@

Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life. Supplementary Figure \@ref(fig:figS10) provides a visualization of mean "scores" for each domain of mental life. To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensation_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age. As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensation_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.

@@

```{r figS10 code, fig.width = 8, fig.asp = 0.5}
d1_gam %>%
  group_by(ResponseId, target_year, factor) %>%
  # # ALTERNATIVE: take just top 5 items per factor (like Study 2)
  # left_join(d1_scales %>% distinct(factor, capacity, loading)) %>%
  # top_n(5, loading) %>%
  summarise(score = mean(response, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = target_year, y = score, color = factor)) +
  facet_grid(~ factor) +
  geom_path(aes(group = ResponseId),
            # color = "#160072",
            alpha = 0.2, size = 0.02) +
  geom_path(
    data = . %>%
      group_by(factor, target_year) %>%
      summarise(mean = mean(score, na.rm = T)) %>%
      ungroup,
    aes(y = mean),
    color = "black", lty = 2) +
  geom_pointrange(
    data = . %>%
      group_by(factor, target_year) %>%
      multi_boot_standard(col = "score") %>%
      ungroup,
    aes(y = mean, ymin = ci_lower, ymax = ci_upper),
    color = "black",
    fatten = 1) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = seq(0, 100, 25)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Mean response\n0 = not at all capable, 100 = completely capable") +
  guides(color = guide_none())

# save plot
if (resave_plots == T | !file.exists("../outputs/figS10.pdf")) {
  ggsave("../outputs/figS10.svg")
  ggsave("../outputs/figS10.pdf")
}
```

```{r figS10, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1). Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
knitr::include_graphics("../outputs/figS10.pdf")
```

@@

```{r figS11 code, fig.width = 9, fig.asp = 0.5}
heatmap_fun(s2_efa_par, 
            factor_names = c("Negative affect",
                             "Cognition and control",
                             "Bodily sensation",
                             "Social connection"))

# save plot
if (resave_plots == T | !file.exists("../outputs/figS11.pdf")) {
  ggsave("../outputs/figS11.svg")
  ggsave("../outputs/figS11.pdf")
}
```

```{r figS11, fig.cap="Study 2, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)", include = F}
knitr::include_graphics("../outputs/figS11.pdf")
```

@@

```{r figS12 code, fig.width = 9, fig.asp = 1.2}
heatmap_fun(s2_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS12.pdf")) {
  ggsave("../outputs/figS12.svg")
  ggsave("../outputs/figS12.pdf")
}
```

```{r figS12, fig.cap="Study 2, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS12.pdf")
```

@@

```{r s2 scales}
d2_scales <- data.frame(
  capacity = colnames(d2_all)) %>%
  mutate(
    factor = case_when(
      capacity %in% c(
        "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
        "feeling_physically_uncomfortable") ~ "Bodily sensation",
      capacity %in% c(
        "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
        "feeling_helpless", "feeling_lonely") ~ "Negative affect",
      capacity %in% c(
        "feeling_happy", "finding_something_funny", "feeling_excited",
        "loving_somebody", "learning_from_other_people") ~ "Social connection",
      capacity %in% c(
        "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
        "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
  mutate(factor = factor(
    factor, 
    levels = c(
      "Bodily sensation", "Negative affect", 
      "Social connection", "Cognition and control"))) %>%
  arrange(factor) %>%
  mutate(loading = NA,
         order = 1:nrow(.))

# # alternatively, could define this based on study 1 data
# d2_scales <- d1_scales %>%
#   filter(capacity %in% colnames(d2_all))

# # alternatively, could define this based on study 2 data
# d2_scales <- s2_efa_par$loadings[] %>%
#   data.frame() %>%
#   rownames_to_column("capacity") %>%
#   gather(factor, loading, -capacity) %>%
#   group_by(capacity) %>%
#   top_n(1, loading) %>%
#   ungroup() %>%
#   mutate(factor = recode_factor(
#     factor,
#     "MR3" = "Bodily sensation",
#     "MR1" = "Negative affect",
#     "MR4" = "Social connection",
#     "MR2" = "Cognition and control")) %>%
#   arrange(factor, desc(loading)) %>%
#   mutate(order = 1:nrow(.))
```

@@

```{r fig04, fig.cap="Network graph summarizing the importance of each developmental mechanism (along the bottom) for each capacity (along the top) among US adults (Study 3). Capacities are sorted and color-coded by domain (see Figures 2-3); developmental mechanisms are arranged in the fixed order of presentation (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social). See main text for the full text of each mechanism. (Identical to Figure 4 in the main manuscript.)", fig.width = 8, fig.asp = 0.8}
d3_mech_ratings_graph <- d3_mech_ratings %>%
  mutate(dev_factor = as.character(dev_factor))

# create nodes dataframe
nodes <- tibble(
  name = c(d2_scales$capacity[d2_scales$capacity %in% unique(d3_mech_ratings$capacity)],
           levels(d3_mech_ratings$dev_factor))) %>%
  mutate(type = ifelse(name %in% d3_mech_ratings_graph$dev_factor, TRUE, FALSE))

# create bipartite graph
g <- graph_from_data_frame(
  d = d3_mech_ratings_graph %>%
    select(capacity, dev_factor, response) %>%
    # filter(!is.na(response), !is.na(dev_factor)) %>%
    group_by(capacity, dev_factor) %>%
    summarise(mean = mean(response, na.rm = T)) %>%
    ungroup(),
  vertices = nodes,
  directed = FALSE
)

# plot network graph
ggraph(g, layout = "bipartite") +
  geom_edge_link(
    aes(width = mean,
        alpha = mean,
        color = mean)) +
  geom_node_point(
    data = . %>%
      mutate(name = factor(name, levels = nodes$name)),
    aes(color = name),
    size = 5) +
  geom_node_text(aes(label = gsub("_", " ", name)),
                 angle = 45,
                 # vjust = -2,
                 hjust = c(rep(0, 8), rep(1, 10)),
                 nudge_x = c(rep(0.05, 8), rep(-0.05, 10)),
                 nudge_y = c(rep(0.05, 8), rep(-0.05, 10)),
                 # nudge_y = c(rep(-1, 8), rep(1, 10)),
                 size = 3) +
  scale_color_manual(
    values = c(rep("#440154FF", 2),
               rep("#35608DFF", 2),
               rep("#22A884FF", 2),
               rep("#BBDF27FF", 2),
               c("#800080", "#8B1A6A", "#990033", "#A0002B", "#BD0026", 
                 "#D31B1C", "#E31A1C", "#F03B20", "#FC4E2A", "#FD8D3C"))
               # rep("#f94802", 10))
  ) +
  # scale_color_manual(
  #   values = c("FALSE" = "black", "TRUE" = "#f94802"),
  #   labels = c("Capacity", "Developmental mechanism"), name = "Node Type") +
  scale_edge_width_continuous(range = c(0.01, 0.7), limits = c(0, 6)) +
  scale_edge_alpha_continuous(range = c(0.05, 1), limits = c(0, 6), breaks = seq(0, 6, 1)) +
  scale_edge_colour_gradient2(
    # low = "gray95", high = "gray70",
    low = "gray90", mid = "gray80", high = "gray10",
    midpoint = 4,
    limits = c(0, 6),
    breaks = seq(0, 6, 1),
    labels = c("0 (not at all important)", 1:5, "6 (extremely important)")) +
  annotate("text", label = "Capacities", 
           x = 5.5, 
           y = Inf, vjust = 1, hjust = 0.5) +
  annotate("text", label = "Developmental mechanisms", 
           x = 5.5, 
           y = -Inf, vjust = -1, hjust = 0.5) +
  scale_x_continuous(limits = c(0, 11)) +
  scale_y_continuous(limits = c(-0.3, 1.3)) +
  theme_minimal() +
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        # plot.background = element_rect(fill = NA, color = "black"),
        legend.position = "right"
        ) +
  guides(edge_width = guide_none(),
         edge_alpha = guide_none(),
         edge_color = guide_edge_colorbar(barwidth = 0.5, barheight = 10),
         color = guide_none()) +
  labs(#title = "Two-Mode Network: Capacities & developmental mechanisms",
       # edge_width = "Mean rating:",
       # edge_alpha = "Mean rating:",
       edge_color = "Mean rating:\n")

# save plot
if (resave_plots == T | !file.exists("../outputs/fig04.pdf")) {
  ggsave("../outputs/fig04.jpg")
  ggsave("../outputs/fig04.svg")
  ggsave("../outputs/fig04.pdf")
}
```

@@

# Study comparison

@@

To provide some sense of the stability and reliability of US adults' representations of specific target ages across studies, Supplementary Figure \@ref(fig:figS13) presents a comparison of capacity ratings at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds). As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here. In Study 2, participants assessed the 20 capacities depicted in Panel A, at 13 target ages (including but not limited to the 3 target ages depicted here). In Study 3, participants assessed 8 capacities (a subset of the 20 capacities depicted in Panel A), at 13 target ages (including but not limited to the 3 target ages depicted here).
